Landau quantization of nearly degenerate bands

### 2018-09-09 paper.tex
Updates from ShareLaTeX
progress

\textbf{A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}

@@

Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation. Hence any symmetry relevant in current context must keep $k_x-k_y$ plane untouched. By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$. Whether the symmetry $g$ transforms the cyclotron orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$. The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point. Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-order in $\A$ needs to be inversed. Besides the transformation of orbits, the transformation of $\H$ is also significant in determining the transformation of $\A$. As a scalar, $\delta\epsilon$ remains intact under the action of $g$ while in contrast $\mathcal{M}$ changes to $(-1)^{u+s}\mathcal{M}$, with $s(g)=0$ (resp. $s(g)=1$) denoting $g$ being unitary (resp. antiunitary). For $\H$ transforming consistently under $g$, $u+s=0, 2$ is required. The indicators defined above classifies symmetry operations into ten and only ten classes, presented in table \ref{table:codimension}.

>>>>

\textbf{A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}
\red{[I begin to question this again. In my previous understanding, the in-plane magnetic field changes the band structure while the out-of-plane magnetic field produces LLs. Now I believe the in-plane magnetic field cannot be simply understood simply as a change in band structures. Therefore, I am not quite sure whether it is related to magnetic breakdown.]}

@@

Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation. Hence any symmetry relevant in current context must keep $k_x$-$k_y$ plane untouched. By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$. Whether the symmetry $g$ transforms the cyclotron orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$. The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point. Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-order in $\A$ needs to be inversed. Besides the transformation of orbits, the transformation of $\H$ is also significant in determining the transformation of $\A$. As a scalar, $\delta\epsilon$ remains intact under the action of $g$ while in contrast $\mathcal{M}$ changes to $(-1)^{u+s}\mathcal{M}$, with $s(g)=0$ (resp. $s(g)=1$) denoting $g$ being unitary (resp. antiunitary). For $\H$ transforming consistently under $g$, $u+s=0, 2$ is required. The indicators defined above classifies symmetry operations into ten and only ten classes, presented in table \ref{table:codimension}.
